%_% These lines starting with %_% are used as annotations for GNU source-highlight package to be able to selectively
%_% convert parts of this file into markup. These can be removed before using this file.
%_% Try: grep -v '^%_%' cheatsheet.tex
%_% Start HEADER
\documentclass[a4paper,extrafontsizes,12pt,twoside,openany]{memoir}
\chapterstyle{bianchi}
\aliaspagestyle{chapter}{empty}
\pagestyle{empty}
%_% End HEADER

%_% PARAGRAPHSTYLES
\setlength\parindent{0in}
\setlength\parskip{1ex}
%_% PARAGRAPHSTYLES

%_% XETEXPACKAGES
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage[dvipsnames,usenames]{xcolor}
%_% XETEXPACKAGES

%_% OTHERPACKAGES
\usepackage{fontspec}
\setromanfont[Mapping=tex-text]{Linux Libertine O}
\usepackage[colorlinks=true,urlcolor=blue,linkcolor=blue]{hyperref}
%_% OTHERPACKAGES

\usepackage{lettrine}
\usepackage{tikz}

\newcommand{\showpart}[1]{\noindent\input{parts/#1}}
\newcommand{\HyperRef}{\href{http://www.tug.org/applications/hyperref/manual.html}{hyperref}\ }
\newcommand{\FontSpec}{\href{http://tug.ctan.org/cgi-bin/ctanPackageInformation.py?id=fontspec}{fontspec}\ }
\newcommand{\TikZ}{\href{http://www.texample.net/tikz/examples/}{PGF/TikZ}\ }

\newcommand{\red}[1]{{\color{red}{#1}}}
\newcommand{\green}[1]{{\color{green}{#1}}}
\newcommand{\blue}[1]{{\color{blue}{#1}}}

\begin{document}

\chapter{The Setup}

\section{The headers}

I use the memoir class here at 12pt default, with the option to work with much higher font sizes. The chapter style,
bianchi, is described in the
\href{ftp://tug.ctan.org/pub/tex-archive/macros/latex/contrib/memoir/memman.pdf}{documentation for the memoir class}.

The pagestyle is empty as I don't want any page numbers. The aliaspagestyle is sort of a hack so that even
chapter-opening pages don't have page numbers.

You might notice that there is a difference in the side margins between pages. This is because of the ``twoside'' option
mentioned above. This makes \LaTeX\ setup the pages for two-side printing by flipping the margins on even and odd pages.

\showpart{HEADER}

\section{Paragraph styling}

The default typesetting of paragraphs in \LaTeX\ is by indentation at the beginning of a paragraph. This has been changed
to no indent and then a bigger gap between the paragraphs, by modifying the \textbackslash{}parskip and \textbackslash{}parindent lengths.

\showpart{PARAGRAPHSTYLES}

\section{\XeTeX\ packages}

Since \XeTeX\ is being used, these three packages are normally included to be able to make the use of Unicode and some additional
functionality easier. The options passed to \href{http://www.ukern.de/tex/xcolor.html}{xcolor} to be able to use of names
instead of color codes are also needed by the \HyperRef package used below.

\showpart{XETEXPACKAGES}

\section{Font setup}

I'm using the wonderful \FontSpec package with
it's brilliant \href{http://tug.ctan.org/tex-archive/macros/xetex/latex/fontspec/fontspec.pdf}{documentation}. Also,
using the \HyperRef package to provide all the links you see in this document.

The main font being used is \href{http://linuxlibertine.sourceforge.net/}{Linux Libertine}. I'll explain what the
Mapping option is for in \autoref{fontspec-mapping}.

\showpart{OTHERPACKAGES}

\chapter{More about fonts}

\section{Ligatures}

\FontSpec understands OpenType \href{http://en.wikipedia.org/wiki/Typographic\_ligature}{ligatures}. Look at the
difference between:

%_% LIGATURES
{\newcommand{\ligs}{O\red{ft}en o\red{ffi}ce o\red{ff}er \red{fj}ord.}
{\Huge {\addfontfeature{Ligatures=NoCommon} \ligs}} \\
{\Huge {\addfontfeature{Ligatures=Rare} \ligs}}}
%_% LIGATURES

This was typeset using: \showpart{LIGATURES}

\section{Mapping}\label{fontspec-mapping}

As you can see below, with the tex-text mapping all the usual quotation marks and the
\href{http://en.wikipedia.org/wiki/Dash#Em\_dash}{em-dashes} are automatically used.

%_% MAPPING
\begin{tabular}{l || l}
No tex-text mapping & {\addfontfeature{Mapping=} No---No" '' ``} \\
With tex-text mapping & {\addfontfeature{Mapping=tex-text} No---No" '' ``}
\end{tabular}
%_% MAPPING

This was typeset using: \showpart{MAPPING}

\section{More font features exposed}

%_% FONTFEATURES
\newcommand{\aff}{\addfontfeature}
\begin{tabular}{l || l}
Qu has a ligature & {\Huge \red{Qu}iet \red{Q}antas} \\
Slashed zero. New style & {\Huge {\aff{Numbers=SlashedZero} 0123456789}} \\
Old style numbers & {\Huge {\aff{Numbers=OldStyle} 0123456789}} \\
Fractions & {\Huge {\aff{Fractions=On} 1/3} vs 1/3} \\
Superiors & {\Huge {\aff{VerticalPosition=Superior}1234567890 Libertine}} \\
More ligatures & {\Huge {\aff{Ligatures=Historical}„\red{st}“ „\red{ct}“}}
\end{tabular}
%_% FONTFEATURES

This was typeset using: \showpart{FONTFEATURES}

\section{Drop caps}

%_% DROPCAP
\renewcommand{\LettrineFontHook}{\color{red!50!white}}
\lettrine[lines=3,loversize=0.2,findent=-2ex,nindent=1ex,slope=1.5ex]{A}{s} you can see, using the
\href{http://tug.ctan.org/cgi-bin/ctanPackageInformation.py?id=lettrine}{lettrine} package, the first letter of this paragraph has been enlarged to ``drop'' down three lines. Drop caps are often seen at the beginning of novels, where the top of the first letter of the first word lines up with the top of the first sentence and drops down to the four or fifth sentence.
%_% DROPCAP

This was typeset using: \showpart{DROPCAP}

\section{Font transparency}

%_% FONTTRANSPARENCY
\begin{tikzpicture}
   \node[scale=3,opacity=0.6]{\red{\HUGE W}};
   \node[scale=3,opacity=0.7,xshift=3ex]{\blue{\HUGE S}};
   \node[scale=3,opacity=0.6,xshift=5ex]{\color{yellow}{\HUGE P}};
   \node[scale=3,opacity=0.4,xshift=7.5ex]{\green{\HUGE R}};
\end{tikzpicture}
%_% FONTTRANSPARENCY

\FontSpec supports font transparency, but it needs some support from the font, apparently. So, enter the brilliant \TikZ
package, with a \href{http://www.ctan.org/tex-archive/graphics/pgf/base/doc/generic/pgf/pgfmanual.pdf}{very
comprehensive manual}.

This was typeset using: \showpart{FONTTRANSPARENCY}

\chapter{Miscallaneous}

\section{stackrel - One above another}

You can put one element above another by using stackrel as mentioned
\href{http://www.uz.ac.zw/science/maths/latex/stackrel.html}{here}:

Do this: \showpart{STACKREL}

It looks like this:
%_% STACKREL
H$_2$CO$_3$ $\stackrel{heat}{\longrightarrow}$ H$_2$O + CO$_2$
%_% STACKREL

\end{document}
